Actuator line modeling of vertical-axis turbines

### 2018-03-31 paper.tex
Add 'the'
Update OF and TF versions

NREL has developed and released an actuator line modeling library,
SOWFA~\cite{Churchfield2014b}, for simulating horizontal-axis wind turbine
arrays using the OpenFOAM finite volume CFD library. OpenFOAM is free,
open-source, widely used throughout industry and academia, and has grown a very
active support community around itself. Though SOWFA is also open-source, its
mostly procedural style would have required significant effort and duplicate
code to adapt for cross-flow turbines. Thus, a new and more general ALM library
was developed from the ground up that could model both cross- and axial-flow
turbines, as well as standalone actuator lines. The actuator line model
developed here, dubbed turbinesFoam \cite{Bachant2016-turbinesFoam-v0.0.7}, was
also written as an extension library for OpenFOAM (version 3.0.x), using its
\texttt{fvOptions} framework for adding source terms to equations at runtime.
This implementation allows the CFT-ALM to be added to many of the standard
solvers included in OpenFOAM without modification, i.e., it can be readily used
with RANS or LES, multiphase models (e.g., for simulating the free surface in
MHK installations), and even with heat transfer.

@@

\authorcontributions{
    P.B. wrote the computer code, ran the simulations, post-processed the
    results, and wrote the paper.
    A.G. contributed to the computer code and the manuscript.
    M.W. contributed to writing and editing of the manuscript.
}

>>>>

NREL has developed and released an actuator line modeling library,
SOWFA~\cite{Churchfield2014b}, for simulating horizontal-axis wind turbine
arrays using the OpenFOAM finite volume CFD library. OpenFOAM is free,
open-source, widely used throughout industry and academia, and has grown a very
active support community around itself. Though SOWFA is also open-source, its
mostly procedural style would have required significant effort and duplicate
code to adapt for cross-flow turbines. Thus, a new and more general ALM library
was developed from the ground up that could model both cross- and axial-flow
turbines, as well as standalone actuator lines. The actuator line model
developed here, dubbed turbinesFoam \cite{Bachant2018-turbinesFoam-v0.0.8}, was
also written as an extension library for OpenFOAM (v5.0), using its
\texttt{fvOptions} framework for adding source terms to equations at runtime.
This implementation allows the CFT-ALM to be added to many of the standard
solvers included in OpenFOAM without modification, i.e., it can be readily used
with RANS or LES, multiphase models (e.g., for simulating the free surface in
MHK installations), and even with heat transfer.

@@

\authorcontributions{
    P.B. wrote the computer code, ran the simulations, post-processed the
    results, and wrote the paper.
    A.G. contributed to the computer code and the manuscript.
    M.W. contributed to the writing and editing of the manuscript.
}
